Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-04-02 document/ms.tex
typos

\hoggtodo{
\kepler\ has been busting out exoplanets (CITE).
Many of them even appear possibly rocky and habitable (CITE).
Nonetheless, none yet known are true Earth analogs.
}

\hoggtodo{
This hasn't stopped anyone from estimating the rate at which Sun-like stars
host Earth-like planets on year-ish period orbits (CITE).
All of these rate estimates are extrapolations of one kind or another.
Here we perform an extremely conservative extrapolation of this kind.
}

\hoggtodo{
What would make an extrapolation like this conservative?
Using \emph{huge bins} does not a conservative estimate make.
You don't want to assume separabilities you can't justify.
You want to explore an enormous function space for the exoplanet rates or pdf.
We are going to do be conservative in these senses here, far more conservative
than anyone who has come before.
}

@@

From our perspective, a ``model'' is a likelihood function---a probability
density (or distribution) function (PDF) for the data given
parameteters---and a set of prior PDFs for the parameters.
In what follows, we will treat as ``data'' a catalog of exoplanet period
and radius measurements (\citealt{petigura}).
\emph{(I don't think need this next sentence).}
We will treat the uncertainties on those measurements as ``prior
information''; that is, we will treat those as true as given and not as being
generated by the parameterized likelihood function.

>>>>

\hoggtodo{%
\kepler\ has been busting out exoplanets (CITE).
Many of them even appear possibly rocky and habitable (CITE).
Nonetheless, none yet known are true Earth analogs.
}

\hoggtodo{%
This hasn't stopped anyone from estimating the rate at which Sun-like stars
host Earth-like planets on year-ish period orbits (CITE).
All of these rate estimates are extrapolations of one kind or another.
Here we perform an extremely conservative extrapolation of this kind.
}

\hoggtodo{%
What would make an extrapolation like this conservative?
Using \emph{huge bins} does not a conservative estimate make.
You don't want to assume separabilities you can't justify.
You want to explore an enormous function space for the exoplanet rates or pdf.
We are going to do be conservative in these senses here, far more conservative
than anyone who has come before.
}

@@

From our perspective, a ``model'' is a likelihood function---a probability
density (or distribution) function (PDF) for the data given
parameters---and a set of prior PDFs for the parameters.
In what follows, we will treat as ``data'' a catalog of exoplanet period
and radius measurements (\citealt{petigura}).
\emph{(I don't think need this next sentence).}
We will treat the uncertainties on those measurements as ``prior
information''; that is, we will treat those as true as given and not as being
generated by the parameterized likelihood function.
